pdp: An R Package for Creating Partial Dependence Plots

### 2016-09-22 manuscript/greenwell.tex
xgboost version warning
final draft

\begin{widefigure}[htbp]
  \centering
  \includegraphics[width=1.0\linewidth]{pd_lstat_rm}
  \caption{Partial dependence of \code{cmedv} on \code{lstat} and \code{rm}. \textit{Left}: Default plot. \textit{Middle}: With contour lines and a different color palette. \textit{Right}: Using a 3-D surface.}
  \label{fig:pd_lstat_rm}
\end{widefigure}

@@

For illustration, we return to the Boston housing data. The code chunk below fits an \pkg{xgboost} model to the \code{boston} data frame from Section~\ref{sec:boston}; the tuning parameters were predetermined using 5-fold cross-validation. (Make sure you are using the latest version of \pkg{xgboost}: \url{https://github.com/dmlc/xgboost/tree/master/R-package}.)
\begin{example}
set.seed(102)  # for reproducibility
boston.xgb <- xgboost(data = data.matrix(subset(boston, select = -cmedv)),
                      label = boston$cmedv, objective = "reg:linear",
                      nrounds = 2000, max_depth = 3, eta = 0.01)
\end{example}

>>>>

\begin{widefigure}[htbp]
  \centering
  \includegraphics[width=1.0\linewidth]{pd_lstat_rm}
  \caption{Partial dependence of \code{cmedv} on \code{lstat} and \code{rm} based on a random forest. \textit{Left}: Default plot. \textit{Middle}: With contour lines and a different color palette. \textit{Right}: Using a 3-D surface.}
  \label{fig:pd_lstat_rm}
\end{widefigure}

@@

For illustration, we return to the Boston housing data. The code chunk below fits an \pkg{xgboost} model to the \code{boston} data frame from Section~\ref{sec:boston}; the tuning parameters were predetermined using 5-fold cross-validation. (Make sure you are using version 0.6-0 or later of \pkg{xgboost}: \url{https://github.com/dmlc/xgboost/tree/master/R-package}.)
\begin{example}
set.seed(102)  # for reproducibility
boston.xgb <- xgboost(data = data.matrix(subset(boston, select = -cmedv)),
                      label = boston$cmedv, objective = "reg:linear",
                      nrounds = 2000, max_depth = 3, eta = 0.01)
\end{example}
